\documentclass[a5paper, 10pt, final]{extreport}
\include{preambule.tex}
\title{Straightforward Pre-intermediate Unit Test 7}
\date{January 23, 2023}
\begin{document}
\maketitle
\tableofcontents
\newpage

\begin{enumerate}
\section{Complete the CV (curriculum vitae) with the correct words or phrases.}
\item PERSONAL DETAILS
\item EDUCATION
\item QUALIFICATIONS
\item PROFESSIONAL EXPERIENCE
\item PERSONAL INTERESTS
\item REFERENCES

\section{Complete sentences 7-12 with an adjective or noun to describe personality. You have the first two letters of the missing words.}
\item intelligence
\item sensitive
\item patience
\item emotion
\item skilled
\item independent

\section{Complete 13-18 with the correct preposition.}
\item for
\item from
\item of
\item for
\item in
\item for

\section{Choose the best word or phrase a, b, or c to complete 19-23.}
\item c
\item b
\item a
\item a
\item c

\section{Complete the sentences. Put the verbs in brackets into the past simple or the present perfect.}
\item have had
\item have never worked
\item have never seen
\item won
\item have never heard
\item Have you ever eaten snake?
\item have been
\item was

\section{Rearrange the words to make questions and statements.}
\item Has Jane arrived at work yet?
\item Have you ever been to Mexico?
\item Has John read his horoscope yet? 
\item I have already applied for this job three times! 
\item I haven't checked my email yet.

\section{Complete the dialogue with phrases from the box.}
\item what should
\item you should
\item you shouldn't
\item should I
\item If I were you
\item what about

\section{Give your friend some advice beginning with the word(s) given.}
\item My hair is too long. I need a haircut. ---
\I{Why don't you get a haircut?}

\item My tooth hurts. ---
\I{If I were you, I'd go to the dentist.}

\item Where's our food? We ordered it 40 minutes ago! ---
\I{What about asking the waiter? }

\item I don't understand the present perfect tense. ---
\I{You should ask the teacher.}

\end{enumerate}
\end{document}