\documentclass[a5paper, 10pt, final]{extreport}
\include{preambule.tex}
\title{Straightforward Pre-intermediate Unit Test 7}
\date{January 27, 2023}
\begin{document}
\maketitlepage

\begin{enumerate}
\section{Choose the best word a, b, or c to complete 1–7.}
\item b
\item a
\item b
\item a
\item c
\item b
\item b

\section{What are the opposites of these adjectives?}
\item impossible
\item dangerous
\item unusual
\item unhealthy
\item illegal

\section{Complete sentences 13-17 with the best adjective from 8-12 and the correct form of the verb in brackets.}
\item It is \Y{illegal to drive} on the right-hand side of the road in Britain.
\item It is \Y{impossible} for humans to live on Mars at the moment.
\item It is \Y{unhealthy} to smoke too many cigarettes.
\item It is \Y{dangerous} to walk home alone at 2 a.m.
\item It is \Y{unusual} to find students who like doing homework!

\section{Put the words in brackets in the correct place in the sentences.}
\item Peter says it will rain tomorrow.
\item If you go now, you won't be late.
\item After they arrive in space they will repair the shuttle
\item Perhaps the rocket will blast off a day later than planned.
\item You will definitely need to take your coat with you.
\item They probably won't arrive before midnight.
\item Before you go, will you call Julie, please?
\item They will be able to come to the party, if they have permission

\section{Correct the mistakes in the sentences.}
\item Maybe Jane feels a bit lonely here on her own.
\item I'll never go into space in a rocket.
\item In one year's time I will have more work and less free time.
\item When everything is ready for the meeting, please call me on my mobile.
\item John says he may not be able to fix the computer.




\section{Match a phrase in column A with a response in column B.}
\item 
\begin{tabular}{ p{6cm} | p{3cm} }
Do you think John will go to the party? & He may do.\\
\end{tabular}
\item
\begin{tabular}{ p{6cm} | p{3cm} }
Will a rocket land on Mars in the near future? & It might do.\\
\end{tabular}
\item
\begin{tabular}{ p{6cm} | p{3cm} }
Please hurry up, Peter! & I won't be long\\
\end{tabular}
\item
\begin{tabular}{ p{6cm} | p{3cm} }
We won't win the football match next weekend. & We may do.\\
\end{tabular}
\item
\begin{tabular}{ p{6cm} | p{3cm} }
Are you unhappy at the moment, Jill? & A little bit, yes.\\
\end{tabular}

\section{Choose the correct verb form to complete 36-40. Are they plans or predictions?}
\item I'm going to
\item I'm going to
\item You'll never
\item I will
\item Are you going to

\section{Translate this instruction into your language.}
\item First of all, connect to the internet.
\item Then, when you are connected, you double click on the email icon.
\item After that, click on ``Write Mail''.
\item Afterwards, type the address of the person you are writing to.
\item The address goes next to the address book icon.
\item Then, write your message in the big space.
\item Next, click on ``Insert'' or ``Attach'' to attach your document to the message.
\item Finally, when the message is ready, click on ``Send'' to send it.
\end{enumerate}
\end{document}