\subsection{Выберите правильный вариант заполнения пропусков в предложениях со сложными предложениями}
\begin{enumerate}
    \item[c] reported
    \item[b] to reach
    \item[a] known
    \item[a] finds
    \item[a] seems to be
    \item[c] to be
    \item[a] appeared
    \item[c] to have
    \item[a] are unlikely to be
    \item[b] is certain
\end{enumerate}

\subsection{Заполните пропуски словами из списка}
\begin{enumerate}
    \item Samuel Morse's hobby was \textbf{} with electricity.
    \item The function of a car computer is \textbf{} and summing up the information about the road conditions.
    \item A new device fer \textbf{monitoring} and adjusting air pressure is tires has recently been developed.
    \item On \textbf{seeing} a red light on a panel and on hearing a warning sound the driver should decrease the speed.
    \item By \textbf{picking} up infrared rays emitted by objects ahead of the car an image-processing system produces different images of objects.
    \item Monitoring and \textbf{} air pressure in tires is one of the new developments of the car designers.
    \item It is difficult to solve some of the present-day scientific and technological problems without \textbf{being} supercomputers.
    \item Upon \textbf{} heated the molecules begin moving very rapidly.
    \item Computers are widely used for \textbf{controlling} all kinds of processes.
    \item Alexander Bell's \textbf{} a teacher of deaf people influenced his interest in sound and its transmission.
\end{enumerate}


\subsection{Переведите предложения с русского на английский язык}

\textbf{1. An electrical circuit is a connection of electrical components performing some useful work and returning to the return path to turn on the charge to its source.}
Электрическая схема представляет собой соединение электрических компонентов, выполняющих какую-то полезную работу и возвращающихся в обратный путь, чтобы включить заряд к своему источнику.

\textbf{2. The components of an electrical circuit can be various elements.}
Компонентами электрической цепи могут быть различные элементы.

\textbf{3. These are such as resistors, capacitors, switches, transformers and electronics.}
Это такие, как резисторы, конденсаторы, переключатели, трансформаторы и электроника.

\textbf{4. Electronic circuits contain active components such as semiconductors and exhibit nonlinear behavior requiring complex analysis.}
Электронные схемы содержат активные компоненты, такие как, полупроводники и демонстрируют нелинейное поведение, требующее комплексного анализа.

\textbf{5. The simplest electrical components are those called passive and linear: while they can temporarily store energy, they do not contain any sources, and exhibit linear responses to stimuli.}
Простейшими электрическими компонентами являются те, которые называются пассивными и линейными: в то время как они могут временно накапливать энергию, они не содержат никаких источников, и демонстрируют линейные реакции на раздражители.

\textbf{6. Semiconductors are widely used in the design of electronic meters, since they react to all types of radiation.}
Полупроводники находят широкое применение при проектировании электронных счетчиков, поскольку они реагируют на все виды излучений.

\textbf{7. One of the main engineering problems that could be solved with the help of semiconductors was the conversion of heat into electricity without the use of boilers or other machines.}
Одной из главных инженерных проблем, которую можно было решить с помощью полупроводников, было преобразование тепла в электричество без использования котлов или других машин.

\textbf{8. It is expected that in a few years the modern aircraft will be replaced by a new model of hypersonic aircraft.}
Ожидается, что через несколько лет современный летательный аппарат будет заменен новой моделью гиперзвукового летательного аппарата.

\textbf{9. It is said that a number of American companies are conducting intensive research in the field of optoelectronic computers.}
Говорят, что в ряде американских компаний ведутся интенсивные исследования в области оптико-электронных вычислительных машин.

\textbf{10. It is known that the method of recording information on a crystal using a laser was developed by a Russian researcher.}
Известно, что метод записи информации на кристалл с помощью лазера был разработан российским исследователем.

\subsection{Переведите предложения с английского на русский}
\textbf{1. Hundreds of radio navigation stations watch the airplanes find their destination and land safely.}
Сотни радионавигационных станций следят за тем, как самолеты находят пункт назначения и благополучно приземляются.

\textbf{2. Nowadays people watch on television cosmonauts' work in space, ``Lunokhod'' move on the surface of the Moon and Olympic Games take place on the other side of the globe.}
В  наши дни люди смотрят по телевизору работу космонавтов в космосе, движение «Лунохода» по поверхности Луны, а Олимпийские игры проходят на другой стороне земного шара.

\textbf{3. A force applied to a body causes it to move in a straight line.}
Сила, приложенная к телу, заставляет его двигаться по прямой линии.

\textbf{4. To develop a new submersible craft with a manipulator is not an easy task.}
Разработать новое подводное судно с манипулятором -- непростая задача.

\textbf{5. To develop the supercomputer, highly developed electronics and new materials were required.}
Для разработки суперкомпьютера требовалась высокоразвитая электроника и новые материалы.

\textbf{6. Our technological advances make it possible to deal with the most difficult problems.}
Наши технологические достижения позволяют решать самые сложные проблемы.

\textbf{7. Some scientists and engineers are working at improving traditional production processes, others are developing new technologies.}
Некоторые ученые и инженеры работают над улучшением традиционных производственных процессов, другие разрабатывают новые технологии.

\textbf{8. A special electronic device signals the engine to stop.}
Специальное электронное устройство подает сигнал двигателю об остановке.

\textbf{9. In a new Japanese car the information to be received by the driver will come through a navigation earth satellite.}
В новом японском автомобиле информация, которую должен получать водитель, будет поступать через навигационный спутник Земли.

\textbf{10. We expect that in the future photon computers will appear and that computations will be
done by means of light.}
Мы ожидаем, что в будущем появятся фотонные компьютеры и что вычисления будут выполняться с помощью света.